Equalizer\\Programming and User Guide

### 2013-01-11 Developer/ProgrammingGuide/paper.tex
Fix file paths

{\footnotesize\lstinputlisting[firstline=142, lastline=158]
  {../../../Equalizer/libs/eq/client/agl/window.cpp}}

@@

{\footnotesize\lstinputlisting[firstline=70, lastline=104]
  {../../../Equalizer/libs/eq/client/glx/window.cpp}}

@@

{\footnotesize\lstinputlisting[firstline=185, lastline=229]
  {../../../Equalizer/libs/eq/client/wgl/window.cpp}}

@@

The network library is implemented in the \textsf{co} namespace. It provides
networking functionality of different abstraction layers, gradually providing
higher level functionality for the programmer. The main primitives in Collage
are:

\begin{description}
\item[Connection] A stream-oriented point-to-point communication
  line. Different implementations of a connection exist.
\item[Node/LocalNode] The abstraction of a process in the cluster. Nodes
  communicate with each other using connections. A LocalNode listens on various
  connections and processes requests for a given process. A Node is a proxy for
  a remote LocalNode.
\item[Object] Provides object-oriented data distribution of C++ objects between
  nodes within a session. Objects are registered or mapped on a LocalNode.
\end{description}

>>>>

{\footnotesize\lstinputlisting[firstline=142, lastline=158]
  {../../../Equalizer/eq/client/agl/window.cpp}}

@@

{\footnotesize\lstinputlisting[firstline=70, lastline=104]
  {../../../Equalizer/eq/client/glx/window.cpp}}

@@

{\footnotesize\lstinputlisting[firstline=185, lastline=229]
  {../../../Equalizer/eq/client/wgl/window.cpp}}

@@

The network library is a separate project on github, implemented in the
\textsf{co} namespace. It provides networking functionality of different
abstraction layers, gradually providing higher level functionality for the
programmer. The main primitives in Collage are:

\begin{description}
\item[Connection] A stream-oriented point-to-point communication
  line. Different implementations of a connection exist. The connections
  transmit raw data reliably between two endpoints for unicast connections, and
  between a set of endpoints for multicast connections.
\item[DataOStream] Abstracts the output of C++ data types onto a
  set of connections by implementing output stream operators. Uses buffering to
  aggregate data for network transmission.
\item[OCommand] Extends DataOStream, implements the protocol between Collage
  nodes.
\item[DataIStream] Decodes a buffer of received data into C++ objects and PODs
  by implementing input stream operators. Performs endian swapping if requested.
\item[ICommand]
\item[Node/LocalNode] The abstraction of a process in the cluster. Nodes
  communicate with each other using connections. A LocalNode listens on various
  connections and processes requests for a given process. A Node is a proxy for
  a remote LocalNode.
\item[Object] Provides object-oriented data distribution of C++ objects between
  nodes within a session. Objects are registered or mapped on a LocalNode.
\end{description}
